---
title       : Shiny app
subtitle    : Gas consumption model
author      : Pablo Garcia
job         : Coursera student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

The goal of this model is computing a gas consumption estimate using only two
variables, one qualitative and one quantitative.
The shiny app computes a linear model based on these variables.
The model is computed with data from the mtcars dataset fron the datasets R package.

Quantitative:
* Weight (lb/1000)
* Displacement (cu.in.)
* Gross horsepower

Qualitative:
* Number of cylinders
* Transmission type
* Number of forward gears

--- .class #id 

## Model selection

Chossing two mentioned variables and the degree of the polynom built with 
quantitive variable a linear model is computed. Lets assume weight, cylinders and quadratic model are selected. The model will perform the following computation:

```{r}
modelFit <- lm( mpg ~ as.factor(cyl) + poly(wt, degree = 2), data = mtcars)
```

--- .class #id

## Visualization

A plot of selected model is included to help choosing between different model based on exploratory analysis.

```{r, echo = FALSE}
c <- as.factor(mtcars$cyl)
x <- mtcars$wt
xRange <- range(mtcars$wt)

plot(mpg ~ wt, data = mtcars, col = c,
         xlab = "Weigth (lb/1000)", ylab = "Miles/(US) gallon",
         main = "Gas consumption model")
    legend(x = "topright",
           pch = rep(1, length(levels(c)) ),
           col = labels(c),
           title = "Cylinders",
           legend = levels(c))
    legend(x = "bottomleft",
           title = "Model type",
           legend = "Quadratic" ) 
    
    gasFit <- lm(mpg ~ poly(x, degree = 2, raw = TRUE) + c, data = mtcars)

    for (i in 1:length(levels(c))) {
      xValues <- seq(xRange[1], xRange[2], length.out = 30)
      xFactor <- rep(levels(c)[i],  30)
      
      xDf <- data.frame(x = xValues, c = xFactor)
  
      results <- predict(gasFit, newdata = xDf)
  
      lines(xValues, results, col = labels(c)[i])
      
    }
```


--- .class #id

## Input values and results
Finally inputing the values for selected variables will compute gas consumption
estimate and also adjusted R-squared to assess goodness of computed model. 

```{r}
    
format(predict(modelFit, newdata = data.frame(wt = 2, cyl = "6")), digits = 1, nsmall = 2)
format(summary(modelFit)$adj.r.squared, digits =1, nsmall = 3)
```


